Supporting Information

### 2022-03-23 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
edits

latitude <- c("42.315336", #1
              "52.762395", #2
              "56.0725",
              "68.35", #4
              "27.90139", #5
              "-36.45", #6
              "71", #7
              "39.4", "-20.25", #8
              "45.4", #9
              "-21.701111", #10
              "-4.67",
              "37.234966", #12bart
              "-4.666667", #13
              "-20.4538",
              "-32.008985", #15
              "39.278958",
              "-43.035889",
              "56.066667")

@@

ggplot(data = world) +
  geom_sf(fill="antiquewhite", color="grey49") +
  xlab("Longitude") + ylab("Latitude") +
  geom_jitter(data=d , aes(longitude,latitude, color=id), 
              shape = 10,  fill = "white",size = 4, 
              stroke = 1,width = 0.2, height = 3)+ 
  theme(panel.grid.major = element_line(color = gray(.5), 
linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
  scale_x_continuous(breaks = c(-100,0, 100)) +
  theme(legend.key.size = unit(0.3, 'cm'), legend.text = element_text(size=6),
         legend.title = element_text(size=12))+
  scale_colour_discrete(name = "Study \n locations")

>>>>

latitude <- c("42.315336", #1
              "52.762395", #2
              "56.0725",
              "68.35", #4
              "27.90139", #5
              "-36.45", #6
              "71", #7
              "39.4", "-23.25", #8 #modified for visibility of ovelapping
              "45.4", #9
              "-21.701111", #10
              "-7.67",#11 #modified for visibility of ovelapping
              "37.234966", #12bart
              "-4.666667", #13
              "-20.4538",
              "-32.008985", #15
              "39.278958",
              "-43.035889",
              "59.066667")#18 #modified for visibility of ovelapping

@@

#these colors come from the library(pals)- labs = c('alphabet')

colors <- c("#FFA405", "#0075DC", "#993F00", "#4C005C", "#5EF1F2", 
        "#005C31", "#2BCE48", "black", "lightblue", "#94FFB5", 
        "#8F7C00", "#9DCC00", "#C20088", "#003380", "gold1", 
        "#FFA8BB", "#426600", "#FF0010", "#191919")

set.seed(12)
ggplot(data = world) +
  geom_sf(fill="antiquewhite", color="grey49") +
  xlab("Longitude") + ylab("Latitude") +
  geom_point(data=d , aes(longitude,latitude,  color=id),  shape=10,
           size = 3.5, stroke=1)+ 
  theme(panel.grid.major = element_line(color = gray(.5), 
linetype = "dashed", size = 0), panel.background = element_rect(fill = "aliceblue"))+
  coord_sf(expand = FALSE) +  scale_y_continuous(breaks = c(-50,0, 50)) +
  scale_x_continuous(breaks = c(-100,0, 100)) +
  theme(legend.key.size = unit(0.5, 'cm'), legend.text = element_text(size=6),
         legend.title = element_text(size=12))+
  scale_colour_discrete(name = "Study \n locations") +   scale_colour_manual(
    values = colors)
